\documentclass{article}
\usepackage{enumitem} % For customizing lists
\usepackage[a4paper,left=26mm,top=36mm,right=26mm,bottom=15mm]{geometry}
\usepackage[usenames, dvipsnames]{color}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{longfbox}
\usepackage{fontawesome}
\usepackage{xcolor}

\makeatletter
\newdimen\@tempdimd
\makeatother
\graphicspath{ {./images/} }

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue, % Adjust the color to your preference
}


\begin{document}

    \pagenumbering{gobble}
    \title{ \raggedright
            \Huge{\vspace{-3.5cm} \color{NavyBlue}Niko Strongioglou } \\ \small{
            \faPhone \, +41(0)787042239 \\
            \faMapMarker \, Salerstrasse 16, 8050 Zurich \\
                \faGithub \, \href{https://github.com/tonyflow}{github} \quad
                \faLinkedin \, \href{https://www.linkedin.com/in/nikolaos-strongioglou/}{linkedIn} \quad
                \faGlobe \, \href{http://tonyflow.github.io/}{web} \quad
                \faUserSecret \, \href{https://leetcode.com/nikostr/}{leetCode} \quad
                \faEnvelope \, \href{mailto:nikos.strongioglou@gmail.com}{email} \quad
                \faCoffee \, \href{https://amemoiroffailures.hashnode.dev/}{blog}
        }
        }
    \author{}
    \date{}
    \maketitle
    
    \vspace{-1.4cm}
    \noindent
    Technical leader with 10+ years of experience designing large-scale distributed systems and data \newline platforms at global scale. Working across disciplines to deliver strategic impact. 

    %#3890A4

    \section*{\color{NavyBlue}Professional Experience}
    \vspace{-0.5cm} 
    \fboxset{rounded,border-color=black,background-color=\#b1bdb4}%
    {\color{NavyBlue}\hrulefill}

        \begin{flushleft}
            \textbf{\large Lead Software Engineer at ethon.ai}
            {\footnotesize \textcolor{gray}{Zurich, Switzerland}} \hfill \small January 2025 - Present
            \newline
            \textit{Platform team lead (6 engineers). Owning MLOps and data, serving vision, time-series anomaly detection, and causal inference teams.}
            \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
                \item Redesigned company-wide data integration: Introduced a scalable, EKS-based, and configurable worker paradigm that decreased the effort of FDEs from days to hours and expanded the product to new markets.
                \item Established platform standards for raw data parsing and loading pipelines, allowing composeable pre-/post-processing and inference. Support for 100+ data and metadata tables.
                \item Architected infra for fine-tuning vision foundation models using PyTorch and AWS Batch. (\href{https://github.com/facebookresearch/dino}{DINO}, \href{https://github.com/facebookresearch/sam2}{SAM 2})
                \item Designed and developed vision inference pipelines with FastAPI, k8s and Triton (point-to-region, region type identification, anomaly detection/classification) - 2ms runtimes.
                \item Provided technical leadership and oversight for the migration from legacy single-node docker-compose deployments to Amazon EKS.
                \item Guided the architecture of a distributed ML experimentation and evaluation platform (100s of datasets) using DVC, AWS Batch (GPU) with metrics tracking via Aim
                \item Database optimizations: compression (up to 90\%+ or $\approx\,\$200$ savings per customer), query optimization for training data retrieval (minutes to seconds), continuous aggregates using materialized views, \href{https://github.com/cloudnative-pg/cloudnative-pg}{CloudNativePG} using \href{https://www.postgresql.org/about/news/pgpool-ii-460-is-now-released-3028/}{pgpool-II} routing, passive/active and read/write nodes, customer data segmentation.
                \item Defined engineering \& hiring standards by conducting 40+ technical interviews.
            \end{itemize}
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Senior Software Engineer at ethon.ai}
            {\footnotesize \textcolor{gray}{Zurich, Switzerland}} \hfill \small June 2024 - December 2024
            \newline
            \textit{MLOps and data on computer vision pipelines. Member of the visual quality inspection team.}
            \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
                \item Designed and led the implementation of a distributed system for exchanging vision models and anomaly detection results between training servers and edge devices.
                \item Redesigned vision data storage architecture and reduced storage footprint by ~40\%.
                \item Observability standards for vision pipelines, pertaining to ROI scores, defect heatmaps, reference images, annotations, model evaluation, other salient (\href{https://en.wikipedia.org/wiki/Scale-invariant_feature_transform}{SIFT}) features.
                \item Drove improvements to testing infrastructure: UI unit testing, revised integration test framework.
            \end{itemize}
            \lfbox{Python} \lfbox{Go} \lfbox{PostgreSQL} \lfbox{Timescale} \lfbox{FastAPI} \lfbox{Flask} \lfbox{\href{https://docs.nvidia.com/deeplearning/triton-inference-server/user-guide/docs/index.html}{Triton}} \lfbox{Angular} \lfbox{TensorFlow} \lfbox{ONNX} \lfbox{Hydra} \lfbox{CUDA} \lfbox{MQTT} \lfbox{Docker} \lfbox{k8s} \lfbox{\href{https://github.com/kubernetes-sigs/kind}{kind}} \lfbox{\href{https://github.com/devspace-sh/devspace}{DevSpace}} \lfbox{\href{https://github.com/aimhubio/aim}{Aim}} \lfbox{\href{https://github.com/gradio-app/gradio}{Gradio}} \lfbox{\href{https://github.com/treeverse/dvc}{DVC}} \lfbox{PyTorch} \lfbox{Buildkite} \lfbox{ArgoCD} \lfbox{AWS} \lfbox{GCP} \\ [1ex] 
        \end{flushleft}

        
        \begin{flushleft}
            \textbf{\large Senior Software Engineer at 1PlusX/TripleLift} 
            {\footnotesize \textcolor{gray}{Zurich, Switzerland}} \hfill \small May 2020 - April 2024 
            \newline
            \textit{Data management and analytics platform providing multi-dimensional batch and real-time user tracking and profiling. Data consolidation and Audience teams. }
            \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
                \item Led multi-sprint/multi-quarter and cross-team data projects: Mentoring small groups of developers while resolving ambiguity with non-engineering dependencies such as legal, product, customer success and external clients.
                \item Created or maintained 50+ unique data pipelines running on production systems with more than 2PB of daily loads (spawning ~30-40k Spark jobs daily).
                \item Developed and maintained Terraform infra for hundreds of AWS services.
                \item Tag manager ingestion restructuring resulting in a data-set specific size decrease of up to 80\% - while maintaining targeting quality.
                \item Decreased pipeline runtime up to 15\% by introducing batch REST API endpoints.
                \item Defined constracts between data engineering and ML teams, reducing iteration cycles and schema drifts.
                \item Cross-team user ID storage optimization resulting in up to 20\% decrease in Couchbase loads. Load on external APIs was decreased up to 40\%. 
                \item Data privacy pipelines: Access and deletion requests' handling of multiple protocols (GDPR, CCPA).
            \item DSL design for ETL ops: Rich syntax for creating and combining attributes.
            \item Real-time data ingestion infrastructure design able to accommodate 7.5M unique events per second.
            \item E2E user tracking: From cookies and browser-side SDKs to graph-based ID management.
                \item UI work on analytics dashboards, widgets, data pipeline builder.
            \end{itemize}
            \lfbox{Scala} \lfbox{Java} \lfbox{Go} \lfbox{Python} \lfbox{Typescript} \lfbox{Angular 2+} \lfbox{Redux} \lfbox{Akka} \lfbox{Spark} \lfbox{\href{https://github.com/spotify/luigi}{Luigi}} \lfbox{AWS} \lfbox{EMR} \lfbox{ECS} \lfbox{EC2} \lfbox{ECR} \lfbox{EKS} \lfbox{RDS} \lfbox{s3} \lfbox{CloudWatch} \lfbox{Kafka} \lfbox{Docker} \lfbox{Terraform} \lfbox{\href{https://github.com/hashicorp/packer}{Packer}} \lfbox{Grafana} \lfbox{InfluxDB} \lfbox{Couchbase} \lfbox{DynamoDB} \lfbox{PostgreSQL} \lfbox{Databricks} \lfbox{Elasticsearch} \lfbox{OpenSearch}\\ [1ex] 
        \end{flushleft}

        \begin{flushleft}
        \textbf{\large Software Engineer at Veezoo AG} {\footnotesize \textcolor{gray}{Zurich, Switzerland}} \hfill \small March 2019 - May 2020   
            \newline
        \textit{NLP platform providing analytics through a variety of corporate data source integrations - namely Oracle, MySQL, PostgreSQL, Salesforce, IBM DB2, Hadoop, SAP HANA - using a QA interface.}
            \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
                \item Knowledge graph ontology representations API for (non)-relational data sources which automated data onboarding.
                \item Semantic parsing pipelines for natural languages (bag of words to logical forms to SQL generation).
                \item Extend and maintain the Duckling language engine.
            \end{itemize}
        \lfbox{Scala} \lfbox{Play} \lfbox{\href{https://github.com/apache/jena}{Apache Jena}} \lfbox{MySQL}          \lfbox{PostgreSQL} \lfbox{Solr} \lfbox{Haskell} \lfbox{Docker} \lfbox{OpenShift} \lfbox{\href{https://github.com/facebook/duckling}{Duckling}} \\ [1ex] 
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Software Engineer at Locatee AG} {\footnotesize \textcolor{gray}{Zurich, Switzerland}} \hfill \small April 2017 - March 2019  \newline 
        \textit{Analytics platform providing hyper-location, real-time workspace occupancy insights and, predictive APIs through geospatial data scraping (SNMP protocol). }
            \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
                \item Led the modularization of the core app monolith. From creating three distinct services - Analytics API, Data processing service, and pollers - to POCs and eventually to global roll-outs.
                \item Online data distillation pipeline detecting outliers on workspace behavior and identifying team collaboration coefficients.
                \item Different MySQL read/write optimizations for measurements post-processing
            \end{itemize}
        \lfbox{Java 8} \lfbox{Spring Core} \lfbox{MySQL} \lfbox{InfluxDB} \lfbox{Tableau} \lfbox{Neo4J}      \lfbox{Kafka} \lfbox{Python} \lfbox{Jupyter} \lfbox{Pandas} \lfbox{Docker} \\ [1ex]
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Software Engineer at Upstream Systems SA} {\footnotesize \textcolor{gray}{Athens, Greece}} \hfill \small October 2014 - March 2017   \newline 
          \textit{Green-field project re-engineering the core CRM monolith as a fully distributed system. The implementation included a multitude of APIs for data streaming and job scheduling accommodating thousands to millions of transactions daily.} 
            
            \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
                \item Asynchronous event-driven services on distributed environments using Guava and RabbitMQ. High availability and resiliency optimizations.
            \item Implementation of Elasticsearch user samplers via Groovy scripts and custom treemap algorithms. Stretch testing, benchmarking, and performance tweaking on Elasticsearch operations.
            \item Performance profiling (Dropwizard’s Metrics, YourKit, Grafana, and other tools).
            \item API versioning (URL \& Resource Representation).
            \item Batch job framework implementation with RabbitMQ and Quartz. Throttling and flow control features included.
                \item QA Automation framework (Selenium, Spring).
            \item \href{https://github.com/tonyflow/recommender}{Recommendation engine} using Mahout and supervised learning regression algorithms (Log Likelihood Similarity for item-based recommender and Pearson correlation similarity for user-based recommender).
            \end{itemize}
        \lfbox{Java 8} \lfbox{Spring Core} \lfbox{Spring Boot} \lfbox{Spring JPA} \lfbox{Spark}       \lfbox{TestNG} \lfbox{RabbitMQ} \lfbox{PostgreSQL} \lfbox{EhCache} \lfbox{Guava} \lfbox{\href{https://github.com/quartz-scheduler/quartz}{Quartz}} \lfbox{\href{https://github.com/flyway/flyway}{flyway}} \lfbox{Hibernate} \lfbox{Elasticsearch} \lfbox{\href{https://github.com/apache/camel}{Camel}} \lfbox{Kafka} \lfbox{Spark} \lfbox{Redis} \lfbox{Docker} \lfbox{Ansible} \lfbox{Protobuf} \\ [1ex]
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Software Engineer at Accenture} {\footnotesize \textcolor{gray}{Athens, Greece}} \hfill \small June 2014 - September 2014  \newline
        \textit{Provisioning and mediation over Oracle databases and mobile telecom software. } \par
        \lfbox{\href{https://www.quest.com/products/toad-for-oracle/}{TOAD}} \lfbox{\href{https://www.oracle.com/database/sqldeveloper/}{SQL Developer}} \lfbox{\href{https://www.oracle.com/java/weblogic/}{WebLogic}} \\ [1ex]
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Freelancing Web Developer} {\footnotesize \textcolor{gray}{Athens, Greece}} \hfill \small January 2012 - November 2013 \newline
        \textit{Software development on static content pages and web applications.}\par
        \lfbox{HTML / CSS} \lfbox{Bootstrap} \lfbox{JavaScript} \lfbox{jQuery} \lfbox{AngularJS} \\ [1ex]
        \end{flushleft}
    
    \vspace{+0.5cm}
    % \begin{multicols}{2}
    
        \section*{\color{NavyBlue}Other Works}
        \vspace{-0.5cm}
        {\color{NavyBlue}\hrulefill}
        \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
            \item Designer and developer of a \href{https://github.com/tonyflow/b-RDBMS}{B+ indexed RDBMS in C}.
            \item Co-creator of a \href{https://github.com/tonyflow/mutiny}{social network} based on node.js and socket.io. The network provided real-time chatting and financial transactions between users.
                \item Prototypes for content moderation and text search using Flask and FastAPI. \href{https://github.com/tonyflow/content-moderator-api}{[1]} \href{https://github.com/tonyflow/natural-language-search-api}{[2]}
            \end{itemize}
                
    % \end{multicols}

        \section*{\color{NavyBlue} Education}
    \vspace{-0.5cm}
    {\color{NavyBlue} \hrulefill}
    
    \subsection*{Degrees}
    \begin{tabular}{p{2cm}  p{12cm}}
        \small September 2013 & \textbf{M.Sc. in Computer Science} \newline
            Department of Computer Science, National and Kapodistrian University of Athens - 7.49/10 or Upper Second-Class Honours
    \end{tabular}

    \subsection*{Languages}
        \begin{tabular}{p{2cm}  p{12cm}}
            Greek & Native \\
            English & Certificate of Proficiency in English, University of Cambridge, Grade A \newline
                            Certificate of Proficiency in English, University of Michigan, Honors \\
            German & B1 \\
            French & Diplome d’etudes en langue Francaise (DELF) 
        \end{tabular}

        \section*{\color{NavyBlue}Conferences}
        \vspace{-0.5cm}
    {\color{NavyBlue} \hrulefill}
        \begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}, leftmargin=1.5em, labelsep=0.3em]
            \item \href{https://mlopsworld.com/}{MLOps World} 2025 
        \end{itemize}
    \section*{\color{NavyBlue}References}
    \vspace{-0.5cm}
    {\color{NavyBlue}\hrulefill} \\
    Available upon request

\end{document}