\documentclass{article}
%\usepackage[a4paper,total={6in,8in}]{geometry}
\usepackage[a4paper,left=26mm,top=36mm,right=26mm,bottom=15mm]{geometry}

%https://tex.stackexchange.com/questions/161877/too-many-white-space-in-bottom-of-the-pages
\usepackage[usenames, dvipsnames]{color}
%https://www.sharelatex.com/learn/Using_colours_in_LaTeX
\usepackage{hyperref}
%https://www.sharelatex.com/learn/Hyperlinks
\usepackage{longtable}
%https://tex.stackexchange.com/questions/26462/make-a-table-span-multiple-pages
\usepackage{multicol}
%https://www.sharelatex.com/learn/Multiple_columns
%\usepackage{enumitem}
%https://tex.stackexchange.com/questions/43743/how-to-reduce-line-space-leading-within-an-enumerate-environment
\usepackage{graphicx}
\usepackage{longfbox}
\usepackage{fontawesome}

\makeatletter
\newdimen\@tempdimd
\makeatother
\graphicspath{ {./images/} }

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue, % Adjust the color to your preference
}

\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.shapes}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{decorations.fractals}
\usetikzlibrary{decorations.footprints}

\tikzset {
    , bedknobs one/.style = {
        decorate
        , fill = red!50
        , decoration = {
            shape backgrounds
            , shape = #1
            , shape size = 2mm
        }
    }
    , bedknobs two/.style = {
        decorate
        , decoration = {
            #1
        }
        , fill = blue!50
    }
}

\newcommand{\bedknobstwo}[1]{
    \begin{center}
        \tikz \draw [bedknobs two = {#1}] (0,0) to (0.5\linewidth, 0);
    \end{center}
}


\begin{document}

	\pagenumbering{gobble}
	\title{ \raggedright
            \Huge{\vspace{-3.5cm} \color{NavyBlue}Niko Strongioglou } \\ \small{
			\faPhone \, +41(0)787042239 \\
			\faMapMarker \, Salerstrasse 16, 8050 Zurich \\
                \faGlobe \, \href{http://tonyflow.github.io/}{web} \quad
                \faLinkedin \, \href{https://www.linkedin.com/in/nikolaos-strongioglou/}{linkedIn} \quad
                \faGithub \, \href{https://github.com/tonyflow}{github} \quad
                \faUserSecret \, \href{https://leetcode.com/nikostr/}{leetCode} \quad
                \faEnvelope \, \href{mailto:nikos.strongioglou@gmail.com}{email}
		}
        }
	\author{}
	\date{}
	\maketitle
	
	\vspace{-1.4cm}
	\noindent
	I am a software engineer with 10 years of experience building large-scale, data-intensive, distributed systems. I revel in being a member of teams composed of smart, self-motivated, and inspired people who consider Computer Science as a means of changing the world.

    %#3890A4

	\section*{\color{NavyBlue}Professional Experience}
	\vspace{-0.5cm}	
	\fboxset{rounded,border-color=black,background-color=\#b1bdb4}%
	{\color{NavyBlue}\hrulefill}
	
	%https://en.wikibooks.org/wiki/LaTeX/Tables
        % \setlength{\LTleft}{-1cm} % Adjust the value (-1cm in this example) to decrease the left margin


        \begin{flushleft}
            \textbf{\large Senior Software Engineer at 1PlusX/TripleLift} \textit{\footnotesize Zurich, Switzerland} \hfill \small May 2020 - Present \newline
            Data management and analytics platform providing multi-dimensional batch and real-time user tracking and profiling. Data consolidation and Audience teams. 
            \newline
            \begin{itemize}
                \item Management of various multi-sprint/multi-quarter and cross-team data projects: Leading and mentoring small groups of developers while resolving ambiguity with non-engineering dependencies (e.g. legal, product, customer success, external clients)
                \item Created or maintained 50+ unique data pipelines running on production systems with more than 2PB of daily loads (spawning ~30-40k Spark jobs daily).
                \item Extensive work on AWS. Developed and maintained Terraform infra of hundreds of services.
                \item Tag manager ingestion restructuring resulting in a data-set specific size decrease of up to 80\% - while maintaining targeting quality.
                \item Decreased pipeline runtime up to 15\% by introducing batch REST API endpoints.
                \item Close collaboration with ML engineers to deliver useful data for their pipelines - MLOps.
                \item Cross-team user ID storage optimization resulting in up to 20\% decrease in Couchbase loads. Load on external APIs was decreased up to 40\%. 
                \item Data privacy pipelines: Access and deletion requests' handling multiple protocols (GDPR, CCPA) both in batch and real-time.
			\item DSL design for ETL ops: Rich syntax for creating and combining attributes.
			\item Real-time data ingestion infrastructure design able to accommodate 7.5M unique events per second.
			\item E2E user tracking: From cookies and browser-side SDKs to graph-based ID management.
                \item UI work on analytics dashboards, widgets, data pipeline builder.
            \end{itemize}
            \lfbox{Scala} \lfbox{Java} \lfbox{Go} \lfbox{Python} \lfbox{Typescript} \lfbox{Angular 2+} \lfbox{Redux} \lfbox{Akka} \lfbox{Spark} \lfbox{Luigi} \lfbox{AWS} \lfbox{EMR} \lfbox{ECS} \lfbox{EC2} \lfbox{ECR} \lfbox{EKS} \lfbox{RDS} \lfbox{S3} \lfbox{CloudWatch} \lfbox{Kafka} \lfbox{Docker} \lfbox{Terraform} \lfbox{Packer} \lfbox{Grafana} \lfbox{InfluxDB} \lfbox{Couchbase} \lfbox{DynamoDB} \lfbox{PostgreSQL} \lfbox{Databricks} \lfbox{Elasticsearch} \lfbox{Opensearch}\\ [1ex] 
        \end{flushleft}

        \begin{flushleft}
	   \textbf{\large Software Engineer at Veezoo AG} \textit{\footnotesize Zurich, Switzerland} \hfill \small March 2019 - May 2020   \newline
		NLP platform providing analytics through a variety of corporate data source integrations - namely Oracle, MySQL, PostgreSQL, Salesforce, IBM DB2, Hadoop, SAP HANA - using a QA interface.
            \newline
            \begin{itemize}
                \item Knowledge graph ontology representations API for (non)-relational data sources which automated data onboarding.
                \item Semantic parsing pipelines for natural languages (bag of words to logical forms to SQL generation).
                \item Extend and maintain the \href{https://github.com/facebook/duckling}{Duckling} language engine
            \end{itemize}
		\lfbox{Scala} \lfbox{Play} \lfbox{Apache Jena} \lfbox{MySQL} \lfbox{PostgreSQL} \lfbox{Solr} \lfbox{Haskell} \lfbox{Docker} \lfbox{OpenShift} \lfbox{Duckling} \\ [1ex] 
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Software Engineer at Locatee AG} \textit{\footnotesize Zurich, Switzerland} \hfill \small April 2017 - March 2019  \newline 
		Analytics platform providing hyperlocation, real-time workspace occupancy insights and predictive APIs through geospatial data scraping (SNMP protocol). 
            \newline
            \begin{itemize}
                \item Led the modularization of the core app monolith. From creating three distinct services - Analytics API, Data processing service, and pollers - to POCs and eventually to global roll-outs.
                \item Online data distillation pipeline detecting outliers on workspace behavior and identifying team collaboration coefficients.
                \item Different MySQL read/write optimizations for measurements post-processing
            \end{itemize}
		\lfbox{Java 8} \lfbox{Spring Core} \lfbox{MySQL} \lfbox{InfluxDB} \lfbox{Tableau} \lfbox{Neo4J}      \lfbox{Kafka} \lfbox{Python} \lfbox{Jupyter} \lfbox{Pandas} \lfbox{Docker} \\ [1ex]
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Software Engineer at Upstream Systems SA} \textit{\footnotesize Athens, Greece} \hfill \small October 2014 - March 2017   \newline 
		Green-field project re-engineering the core CRM platform as a fully distributed system. The implementation included a multitude of APIs for data streaming and job scheduling accommodating thousands to millions of transactions daily. 
            \newline
            \begin{itemize}
                \item Asynchronous event-driven services on distributed environments using Guava and RabbitMQ. High availability and resiliency optimizations.
			\item Implementation of Elasticsearch user samplers via Groovy scripts and custom treemap algorithms. Stretch testing, benchmarking, and performance tweaking on Elasticsearch operations.
			\item Performance profiling (Dropwizard’s Metrics, YourKit, Grafana, and other tools).
			\item API versioning (URL \& Resource Representation).
			\item Batch job framework implementation with RabbitMQ and Quartz. Throttling and flow control features included.
                \item QA Automation framework (Selenium, Spring).
			\item Recommendation engine using Mahout and supervised learning regression algorithms (Log Likelihood Similarity for item-based recommender and Pearson correlation similarity for user-based recommender).
            \end{itemize}
		\lfbox{Java 8} \lfbox{Spring Core} \lfbox{Spring Boot} \lfbox{Spring JPA} \lfbox{Spark}       \lfbox{TestNG} \lfbox{RabbitMQ} \lfbox{PostgreSQL} \lfbox{EhCache} \lfbox{Guava} \lfbox{Quartz} \lfbox{Flyway} \lfbox{Hibernate} \lfbox{Elasticsearch} \lfbox{Camel} \lfbox{Kafka} \lfbox{Spark} \lfbox{Redis} \lfbox{Docker} \lfbox{Ansible} \lfbox{Protobuf} \\ [1ex]
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Software Engineer at Accenture} \textit{\footnotesize Athens, Greece} \hfill \small June 2014 - September 2014  \newline
		Provisioning and mediation over Oracle databases and mobile telecom software. \newline
		\lfbox{TOAD} \lfbox{SQL Developer} \lfbox{WebLogic} \\ [1ex]
        \end{flushleft}

        \begin{flushleft}
            \textbf{\large Freelancing Web Developer} \textit{\footnotesize Athens, Greece} \hfill \small January 2012 - November 2013 \newline
		Software development on static content pages and web applications. \newline
		\lfbox{HTML / CSS} \lfbox{Bootstrap} \lfbox{Javascript} \lfbox{jQuery} \lfbox{Angular JS} \\ [1ex]
        \end{flushleft}
	
	\vspace{+0.5cm}
	% \begin{multicols}{2}
	
		\section*{\color{NavyBlue}Other Works}
		\vspace{-0.5cm}
		{\color{NavyBlue}\hrulefill}
		\begin{itemize}
			\item Designer and developer of a B+ indexed RDBMS in C.
			\item Co-creator of a social network based on node.js and socket.io. The network provided real-time chatting and financial transactions between users.
                \item Various API prototypes using Flask and FastAPI
            \end{itemize}
                
	% \end{multicols}

        \section*{\color{NavyBlue} Education}
	\vspace{-0.5cm}
	{\color{NavyBlue} \hrulefill}
	
	\subsection*{Degrees}
	\begin{tabular}{p{2cm}  p{12cm}}
		\small September 2013 & \textbf{M.Sc. in Computer Science} \newline
			Department of Computer Science, National and Kapodistrian University of Athens - 7.49/10 or Upper Second-Class Honours
	\end{tabular}

	\subsection*{Languages}
		\begin{tabular}{p{2cm}  p{12cm}}
			Greek & Native \\
			English & Certificate of Proficiency in English, University of Cambridge, Grade A \newline
							Certificate of Proficiency in English, University of Michigan, Honors \\
			German & B1 \\
			French & Diplome d’etudes en langue Francaise (DELF) 
		\end{tabular}

	\section*{\color{NavyBlue}References}
	\vspace{-0.5cm}
	{\color{NavyBlue}\hrulefill} \\
	Available upon request

\end{document}